### 2021-03-14 README.Rmd
- Added a little info to the citation info. - In the README removed the step where we make sp a factor, because now that happens under-the-hood.

```{r}
growth_ex <-
  compute_growth(
    census_1 = census_1_ex %>% 
      mutate(sp = to_any_case(sp) %>% factor()),
    census_2 = census_2_ex %>% 
      filter(!str_detect(codes, "R")) %>% 
      mutate(sp = to_any_case(sp) %>% factor()),
    id = "ID"
  )
```

>>>>

```{r}
growth_ex <-
  compute_growth(
    census_1 = census_1_ex %>% 
      mutate(sp = to_any_case(sp)),
    census_2 = census_2_ex %>% 
      filter(!str_detect(codes, "R")) %>% 
      mutate(sp = to_any_case(sp)),
    id = "ID"
  )
```
